---
title: "HW17"
output:
  word_document: default
  html_notebook: default
  html_document: default
---

We will keep working on the model from our last assignment, though we will now remove factors that were
insignificant in our prior study:
Reputation (REP) + Policies (POL) + Perceived Website Investment (INV) + Familiarity (FAML) →
Perceived Security (SEC) → Trust (TRUST)
Note: REP, POL, INV, and FAML are antecedents ; SEC is a mediator ; and TRUST is the outcome

```{r}
library(seminr)
sec = read.csv("security_data.csv")

# Measurement Model 
sec_mm <- measure(
  form("REP",multi_items("PREP",1:4)),
  reflect("INV", multi_items("PINV",1:3)),
  reflect("POL", multi_items("PPSS",1:3)),
  reflect("FAML","FAML1"),
  reflect("TRUST", multi_items("TRST", 1:4)),
  reflect("SEC",multi_items("PSEC",1:4))
)


#Structural Model
sec_sm <- structure(
  paths(from = c("REP","INV","POL","FAML"), to = "SEC"),
  paths(from = "SEC", to = "TRUST")
)

#run PLS

sec_pls <- estimate_model(data = sec,
                          measurement_model = sec_mm,
                          structural_model = sec_sm)
```

Question 1) Let’s check the measurement quality criteria for our model.

a). Check item reliability of all factors:
i. Reflective factors: λ > 0.70
“ Do items individually share variance with their proper constructs?”

```{r}
sec_pls$outer_loadings
```

From the above table, we can find out most of the variable share variance with their proper constructs. However, the loadins of PREP1 did not exceed 0.7 !


ii. Formative factors: VIF of items < 5
“Do items individually contribute substantially meaningful variance to their constructs?

```{r}
sec_pls$outer_weights[multi_items("PREP",1:4),"REP"]
```

Check VIF if formaticve items
```{r}
prep1_regr <-lm(sec$PREP1 ~ sec$PREP2 + sec$PREP3 + sec$PREP4)
prep1_r2 <-summary(prep1_regr)$r.squared
prep1_vif <-1 / (1 -prep1_r2)

prep2_regr <-lm(sec$PREP2 ~ sec$PREP1 + sec$PREP3 + sec$PREP4)
prep2_r2 <-summary(prep2_regr)$r.squared
prep2_vif <-1 / (1 -prep2_r2)


prep3_regr <-lm(sec$PREP3 ~ sec$PREP2 + sec$PREP1 + sec$PREP4)
prep3_r2 <-summary(prep3_regr)$r.squared
prep3_vif <-1 / (1 -prep3_r2)


prep4_regr <-lm(sec$PREP4 ~ sec$PREP2 + sec$PREP3 + sec$PREP1)
prep4_r2 <-summary(prep4_regr)$r.squared
prep4_vif <-1 / (1 -prep4_r2)

cat("prep1",prep1_vif,"\nprep2",prep2_vif,"\nprep3",prep3_vif,"\nprep4",prep4_vif)
```

VIF of each items didn't exceed 5.

b). Convergent validity (reflective factors only):

i. Composite Reliability (CR) of factors: CR > 0.70
“How much do the items of a reflect factor agree with one another?”
```{r}
#INV
INV_items<-multi_items("PINV", 1:3)
INV_loadings<-sec_pls$outer_loadings[INV_items, "INV"]
INV_CR <-sum(INV_loadings)^2 / (sum(INV_loadings)^2 + sum(1-INV_loadings)^2)

#POL
POL_items<-multi_items("PPSS",1:3) 
POL_loadings<-sec_pls$outer_loadings[POL_items, "POL"]
POL_CR <-sum(POL_loadings)^2 / (sum(POL_loadings)^2 + sum(1-POL_loadings)^2)

FAML_items<-"FAML1"
FAML_loadings<-sec_pls$outer_loadings[FAML_items, "FAML"]
FAML_CR <-sum(FAML_loadings)^2 / (sum(FAML_loadings)^2 + sum(1-FAML_loadings)^2)

cat("INV CR",INV_CR,"\nPOL CR", POL_CR, "\nFAML CR", FAML_CR)
```

All of the reflective fators' convergent validity are greater than 0.7.

ii. Average Variance Extracted (AVE) of factors: AVE > 0.50
“How much variance, on average, does a reflective factor explain of its own items?”

```{r}
INV_AVE <-sum(INV_loadings^2) / (sum(INV_loadings^2) + sum(1-INV_loadings^2) ) 
POL_AVE <-sum(POL_loadings^2) / (sum(POL_loadings^2) + sum(1-POL_loadings^2) ) 
FAML_AVE <-sum(FAML_loadings^2) / (sum(FAML_loadings^2) + sum(1-FAML_loadings^2) ) 

cat("INV AVE",INV_AVE,"\nPOL AVE", POL_AVE, "\nFAML AVE", FAML_AVE)
```

All of them are greater than 0.5!

c). Discriminant Validity (reflective factors only):

i. Loadings of all items on own factors greater than cross-loadings with other factors
“Are items more correlated with their own factors than other factors?”

```{r}
cat("INV cor\n")
cor(sec[,INV_items], sec_pls$fscores)

cat("\nPOL cor\n")
cor(sec[,POL_items], sec_pls$fscores)

cat("\nFAML cor\n")
cor(sec[,FAML_items], sec_pls$fscores)
```

According to the correlation matrix above, all of the items are more correlated with their own factors.

ii. Correlation of factor with other factors smaller than factor’s square root of AVE
“Is a factor more related to its own items than it is to other factors?”

```{r}
sqrt(INV_AVE)
sqrt(POL_AVE)
sqrt(FAML_AVE)

cor(sec_pls$fscores)
```

Yes, the factors are more related to their own items.

Question 2) Does SEC really mediate relationships between REP, POL, INV → TRUST?

a). With each of the three factors (REP, POL, INV), check the four parts of the mediation analysis we discussed in class

i. Try using three models to test for mediation:

- the proposed model

```{r}
# Measurement Model 
sec_mm <- measure(
  form("REP",multi_items("PREP",1:4)),
  reflect("INV", multi_items("PINV",1:3)),
  reflect("POL", multi_items("PPSS",1:3)),
  reflect("FAML","FAML1"),
  reflect("TRUST", multi_items("TRST", 1:4)),
  reflect("SEC",multi_items("PSEC",1:4))
)


#Structural Model
sec_sm <- structure(
  paths(from = c("REP","INV","POL","FAML"), to = "SEC"),
  paths(from = "SEC", to = "TRUST")
)

#run PLS

boot_sec <- bootstrap_model(data = sec,
                          measurement_model = sec_mm,
                          structural_model = sec_sm)
print_paths(boot_sec)
```

- the proposed model without the mediator

```{r}
# Measurement Model 
sec_mm <- measure(
  form("REP",multi_items("PREP",1:4)),
  reflect("INV", multi_items("PINV",1:3)),
  reflect("POL", multi_items("PPSS",1:3)),
  reflect("FAML","FAML1"),
  reflect("TRUST", multi_items("TRST", 1:4))
)


#Structural Model
sec_sm <- structure(
  paths(from = c("REP","INV","POL","FAML"), to = "TRUST")
)

#run PLS

boot_sec <- bootstrap_model(data = sec,
                          measurement_model = sec_mm,
                          structural_model = sec_sm)
print_paths(boot_sec)
```


- the proposed model with paths from antecedents to outcomes

```{r}
# Measurement Model 
sec_mm <- measure(
  form("REP",multi_items("PREP",1:4)),
  reflect("INV", multi_items("PINV",1:3)),
  reflect("POL", multi_items("PPSS",1:3)),
  reflect("FAML","FAML1"),
  reflect("TRUST", multi_items("TRST", 1:4)),
  reflect("SEC",multi_items("PSEC",1:4))
)


#Structural Model
sec_sm <- structure(
  paths(from = c("REP","INV","POL","FAML"), to = "SEC"),
   paths(from = c("REP","INV","POL","FAML"), to = "TRUST"),
  paths(from = "SEC", to = "TRUST")
)

#run PLS

boot_sec <- bootstrap_model(data = sec,
                          measurement_model = sec_mm,
                          structural_model = sec_sm)
print_paths(boot_sec)
```



ii. When testing each of the three factors (REP, POL, INV), remove the other two factors, but keep FAML as a control

```{r}
# test REP to SEC
# Measurement Model 
sec_mm <- measure(
  form("REP",multi_items("PREP",1:4)),
  reflect("FAML","FAML1"),
  reflect("SEC",multi_items("PSEC",1:4))
)


#Structural Model
sec_sm <- structure(
  paths(from = c("REP","FAML"), to = "SEC")
)

#run PLS

boot_sec <- bootstrap_model(data = sec,
                          measurement_model = sec_mm,
                          structural_model = sec_sm)
print_paths(boot_sec)
```
```{r}
# test POL
# Measurement Model 
sec_mm <- measure(
  reflect("POL", multi_items("PPSS",1:3)),
  reflect("FAML","FAML1"),
  reflect("SEC",multi_items("PSEC",1:4))
)


#Structural Model
sec_sm <- structure(
  paths(from = c("POL","FAML"), to = "SEC")
)

#run PLS

boot_sec <- bootstrap_model(data = sec,
                          measurement_model = sec_mm,
                          structural_model = sec_sm)
print_paths(boot_sec)
```


```{r}
# test INV
# Measurement Model 
sec_mm <- measure(
  reflect("INV", multi_items("PINV",1:3)),
  reflect("FAML","FAML1"),
  reflect("SEC",multi_items("PSEC",1:4))
)


#Structural Model
sec_sm <- structure(
  paths(from = c("INV","FAML"), to = "SEC")
)

#run PLS

boot_sec <- bootstrap_model(data = sec,
                          measurement_model = sec_mm,
                          structural_model = sec_sm)
print_paths(boot_sec)
```

b). Which factors are fully mediated by SEC, which are partially mediated by SEC, and which are not at all mediated by SEC?

From the above model testing, we can conclude that:

POL is fully mediated by SEC. INV and FAML is partially mediated by SEC. REP is not at all mediated by SEC.


