---
title: "HW15"
output:
  word_document: default
  html_notebook: default
---


Question 1) Create a PLS path model using SmartPLS, with the following characteristics:


a).Create a PLS path model using SmartPLS, with the following characteristics:

i. Measurement of constructs by items
  1. Trust in website (TRUST): reflective construct with items TRST1-4
  2. Perceived security of website (SEC): reflective construct with items PSEC1-4
  3. Reputation of website (REP): formative construct with items PREP1-4
  4. Investment in website (INV): reflective construct with PINV1-3
  5. Perception of policy (POL): reflective construct with items PPSS1-3
  6. Familiarity with website (FAML): single-item construct measured by FAML1
ii. Interaction between REP and POL (use orthogonalized product terms)
iii. Structural paths between constructs (shown as causal models -- note direction of arrows):
  1. SEC ← REP + INV + POL + FAML + REP.POL
  2. TRUST ← SEC

```{r}
library(seminr)
sec = read.csv("security_data.csv")

# Measurement Model 
sec_mm <- measure(
  form("REP",multi_items("PREP",1:4)),
  reflect("INV", multi_items("PINV",1:3)),
  reflect("POL", multi_items("PPSS",1:3)),
  reflect("FAML","FAML1"),
  reflect("TRUST", multi_items("TRST", 1:4)),
  reflect("SEC",multi_items("PSEC",1:4))
)

#interaction term
sec_intxn <- interact(
  interaction_ortho("REP","POL")
)

#Structural Model
sec_sm <- structure(
  paths(from = c("REP","INV","POL","FAML","REP.POL"), to = "SEC"),
  paths(from = "SEC", to = "TRUST")
)

#run PLS

sec_pls <- estimate_model(data = sec,
                          measurement_model = sec_mm,
                          structural_model = sec_sm,
                          interactions = sec_intxn)

```

b). Show us the following results in table of figure formats:

i. Loadings of reflective factors / Weights of formative factors

```{r}
sec_pls$outer_loadings
```

```{r}
sec_pls$outer_weights
```

ii. Regression coefficients of paths between factors

```{r}
print_paths(sec_pls)
```

iii. Bootstrapped path coefficients: t-values, p-values (are any paths not significant at p=5% ?)

```{r}
boot_pls <- bootstrap_model(data = sec,
                          measurement_model = sec_mm,
                          structural_model = sec_sm,
                          interactions = sec_intxn,
                          nboot = 1000)
```
```{r}
print_paths(boot_pls)
```

From the above table, we can find out that FAML and REP.POL are insignificant paths.


